A Dependently Typed Multi-Stage Calculus \ifnotanonymous\thanks{Supported by organization x.}\fi

### 2019-06-19 text/introduction.tex
Small changes.
Further revision

In this paper, we develop a new multi-stage calculus \LMD by extending
the existing multi-stage calculus \LTP\cite{Hanada2014}---which
formalizes the four constructs of MetaOCaml in a way slightly
different from MetaOCaml---with dependent types and study its
properties.  We base our work on \LTP because its type system and
semantics are arguably simpler than
\(\lambda^\alpha\)~\cite{taha2003environment}, which is more faithful
to the design of MetaOCaml.  Our technical contribution are summarized
as follows:
\begin{itemize}
\item We give the formal definition of \LMD with its syntax, 
  type system and two kinds of reduction---full and staged reduction.
\item We show preservation, strong normalization, and confluence for
  full reduction; and show unique decomposition (and progress as its
  corollary) for staged reduction, which formalizes program execution.
\end{itemize}
The combination of multi-stage programming and dependent types has
been discussed by Brady and Hammond~\cite{brady2006dependently} but,
to our knowledge, our work is a first formal calculus of dependently
typed multi-stage programming.

\subsection{Organization of the Paper}

>>>>

\subsection{Our Work}
In this paper, we develop a new multi-stage calculus \LMD by extending
the existing multi-stage calculus \LTP\cite{Hanada2014} with dependent
types and study its properties.  We base our work on \LTP, in which
the four multi-stage constructs are handled slightly differently from
MetaOCaml, because its type system and semantics are arguably simpler
than \(\lambda^\alpha\)~\cite{taha2003environment}, another calculus,
which formalizes the design of MetaOCaml more faithfully.  Our
technical contribution are summarized as follows:
\begin{itemize}
\item We give the formal definition of \LMD with its syntax, 
  type system and two kinds of reduction---full and staged reduction.
\item We show preservation, strong normalization, and confluence for
  full reduction; and show unique decomposition (and progress as its
  corollary) for staged reduction, which formalizes program execution.
\end{itemize}
The combination of multi-stage programming and dependent types has
been discussed by Brady and Hammond~\cite{brady2006dependently} but,
to our knowledge, our work is a first formal calculus of dependently
typed multi-stage programming.

\AI{Informal discussion on how important CSP is?}
\AI{Comments on Appendix required.}

\subsubsection{Organization of the Paper.}
